### 2018-07-07 latex/figurelegends.tex
Included changes by Ines
Added Fig S2

\section{Figure Legends}

\subsection{Figure 1}

@@

\subsection{Figure 2}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.75\textwidth]{fig_2_phylo_distribution}
  \caption{\textbf{Evolutionary distribution of NADA, NNMT, and NamPRT and their relation to the number of NAD consumers.} A) Distribution of NADA, NNMT, and NamPRT in selected major taxa. NADA is dominant in Bacteria, Fungi, and Plants (Viridiplantae), whereas NamPRT together with NNMT is dominant in Metazoa. Numbers at the pie charts show, how many species of the taxon possess the respective enzyme combination indicated by the colour, which is explained in the lower right of the figure. Below the taxon name, the number of species in that taxon is given. B) Common tree of selected taxa within the Metazoa, including 334 species. The pie charts indicate the distribution of species within the respective taxon that encode the enzyme combination indicated by the different colours. The size of the pie charts is proportional to the logarithm of the number of species analysed in the particular taxon. The numbers below the taxon names indicate the average number of NAD-consuming enzyme families found in all sub-taxa. The branch length is arbitrary.}
  \label{fig:phylo_distribution}
\end{figure}

@@

\subsection{Figure 3}

@@

\subsection{Figure 4}

@@

\subsection{Figure 5}

@@

\subsection{Figure 6}

@@

\subsection{Figure 7}

@@

\subsection{Figure 8}

>>>>

\section*{Figure Legends}

\subsection*{Figure 1}

@@

\subsection*{Figure 2}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.75\textwidth]{fig_2_phylo_distribution}
  \caption{\textbf{Phylogenetic distribution of NADA, NNMT, and NamPRT and their relation to the number of NAD consumers.} A) Distribution of NADA, NNMT, and NamPRT in selected major taxa. NADA is dominant in Bacteria, Fungi, and Plants (Viridiplantae), whereas NamPRT together with NNMT is dominant in Metazoa. Numbers at the pie charts show, how many species of the taxon possess the respective enzyme combination indicated by the colour, which is explained in the lower right of the figure. Below the taxon name, the number of species in that taxon is given. B) Common tree of selected taxa within the Metazoa, including 334 species. The pie charts indicate the distribution of species within the respective taxon that encode the enzyme combination indicated by the different colours. The size of the pie charts is proportional to the logarithm of the number of species analysed in the particular taxon. The numbers below the taxon names indicate the average number of NAD-consuming enzyme families found in all sub-taxa. The branch length is arbitrary.}
  \label{fig:phylo_distribution}
\end{figure}

@@

\subsection*{Figure 3}

@@

\subsection*{Figure 4}

@@

\subsection*{Figure 5}

@@

\subsection*{Figure 6}

@@

\subsection*{Figure 7}

@@

\subsection*{Figure 8}

### 2018-07-07 latex/supplementaries.tex
Included changes by Ines
Added Fig S2

\section{Supplementary Legends}

\subsection{Supplementary figure S1}

@@

\subsection{Supplementary figure S2}

\todo{Figure must be made!}\textbf{Distribution of NNMT in birds.} ...

\subsection{Supplementary figure S3}

@@

\subsection{Supplementary table S1}

@@

\subsection{Supplementary table S2}

\textbf{Overview of kinetic constants used for the construction of the model.}

>>>>

\section*{Supplementary Legends}

\subsection*{Supplementary figure S1}

@@

\subsection*{Supplementary figure S2}

\textbf{The phylogenetic distribution of NamPRT and NNMT in birds and reptiles is scattered.}

\subsection*{Supplementary figure S3}

@@

\subsection*{Supplementary table S1}

@@

\subsection*{Supplementary table S2}

\textbf{Overview of kinetic constants and rate laws used for the construction of the mathematical model.}
